Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-17 analysis/paper/paper.Rmd
Add statement on how models were selected
Remove software score from figure

The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
Statistical analysis were carried out using R 4.1.0 (R Core Team, 2021), the rstanarm (v2.13.1; Gabry & Goodrich, 2016) and the report (v0.2.0; Makowski, Patil, & Lüdecke, 2019) packages. The full reproducible code is available in Supplementary Materials.

@@

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using cumulative family function for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.

@@

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the three categories evaluated, (A) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used. (B) displays 'Code availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. (C) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}

a <- ggplot(rrpp, aes(x = as.factor(software_avail))) +
  geom_bar(fill = "black") +
  ylab("Count") +
  xlab("Article Score") +
  ggtitle("Software")

b <- ggplot(rrpp, aes(x = as.factor(comp_mthds_avail))) +
  geom_bar(fill = "black") +
  ylab("Count") +
  xlab("Article Score") +
  ggtitle("Code")

c <- ggplot(rrpp, aes(x = as.factor(data_avail))) +
  geom_bar(fill = "black") +
  ylab("Count") +
  xlab("Article Score") +
  ggtitle("Data")

p <- a + b + c
p <- p +
  plot_annotation(tag_levels = "A") &
  theme(text = element_text("Arial"))

>>>>

The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
Statistical analysis were carried out using R 4.1.0 (R Core Team, 2021), the rstanarm (v2.13.1; Gabry & Goodrich, 2016) and the report (v0.2.0; Makowski, Patil, & Lüdecke, 2019) packages. The full reproducible code is available in @Sparks2022.

@@

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using cumulative family function for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log pointwise predictive density via `loo_compare()`.

@@

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the two categories evaluated, (A) displays 'Code availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. (B) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}

a <- ggplot(rrpp, aes(x = as.factor(comp_mthds_avail))) +
  geom_bar(fill = "black") +
  ylab("Count") +
  xlab("Article Score") +
  ggtitle("Code")

b <- ggplot(rrpp, aes(x = as.factor(data_avail))) +
  geom_bar(fill = "black") +
  ylab("Count") +
  xlab("Article Score") +
  ggtitle("Data")
